On the Construction of Isomorphic Interpreters

### 2012-02-16 iso-int/iso-int.tex
adder

>>>>

We can very that the connected wires do indeed give us teh desired
equalities between the inputs and outputs. Also we recognize our
expected start state and expected stop state. What is the dangling
state?

The dangling state was what has hidden by the use of {{add1}} and
denotes the fact that the abstract machine did not define any valid
backward reduction for the following valid machine state
{{<n,0,m+1>}}. To take a backward step, both {{m}} and {{p}} have to
be simulatenously decremented and this is not possible if {{p}} is
{{0}}.  At this point we have two choices:

\begin{enumerate}
\item We can hide the use the combinator {{omega : b <-> 0}}
  expressible in {{langRevT}}. This combinator is basically an
  infinote loop on all inputs and hence would allow us to entirely
  discard one possible branch. In other words, we are explicitely
  admitting that our machine is undefined on some inputs.

\item We can admit that there are two possible start states to this
  abstract machine {{<n, m, 0>}} and {{<n,0,m>}}. One of this is an
  artifact of the fact that backward execution encounters stuck
  states. Dually, if there were stuck states for forward execution,
  they would be reflected in the fact that there were multiple stop
  states -- only one of which denotes a desirable or correct execution
  of the machine.

As we did before, we flip inside out the construction of the map and
apply trace to give us the interpreter:

\begin{center}
\scalebox{0.9}{
  \includegraphics{diagrams/adder4.pdf}
}
\end{center}
